---
title: "IO"
output: html_notebook
---

# Packages and global options

```{r packages}
library(tidyverse)
# library(Biostrings)
library(devtools)
library(stringr)
```


# Importing sequences

The most basic function of this app is importing a sequence file on FASTA format. The imported file can either be the *template* sequence or the *target* sequence. The target sequence is the DNA sequence of the gene of interest that will be inserted into the template sequence. We can create a basic function to import a DNA sequence with two derived functions, one for each type of input:

```{r read-sequence-fun}
read_sequence <- function(file, ...) {
  raw <- as_data_frame(read_file(file))
  
  df <-raw %>%
    separate_rows(value, sep = '\n>') %>%
    separate(value, into = c('header', 'seq'), sep = '\n', extra = 'merge') %>%
    mutate(
      seq = str_replace_all(seq, '\n', ''),
      header = str_replace(header, '>', '')
    )
}

template <- read_sequence("../data/puc19.fasta")
target <- read_sequence("../data/GFP sequence.fasta")
```

# Case 1: insertion of target sequence into template 

We can 


