---
title: "`lambdaPrimeR` analysis notebook"
author: Pedro Ivo Guimarães
output: 
  html_notebook:
    toc: yes
---

```{r libraries-and-options, warning=FALSE, message=FALSE}
library(tidyverse)
library(stringr)
devtools::load_all(pkg = "~/lambdaPrimeR/")
```

# May 

## 05/03/18

### Importing Imen's lambda PCR primers

```{r importing-primers}
path <- system.file('extdata', 'imen_primers.csv', package = "lambdaPrimeR")
imen_primers <- read_csv(path)
```
```{r}
imen_primers
```

We need to isolate the primer sequence into the target and vector annealing 
sequences by splitting the sequence string on the first uppercase character:

```{r}
imen_primers <- imen_primers %>%
  mutate(seq_split = gsub('[[:lower:]]([[:upper:]])', ',\\1', seq)) %>%
  separate(seq_split, into = c('vector_annealing_seq', 'target_annealing_seq'), sep = ',')
```

## 05/04/2018

### Locating insertion position based on primer sequence

I need to locate the insertion position that each target gene was inserted into 
pUC19 based on the sequence of the vector annealing parts of the primer sequences.
We can do this by isolating the vector annealing sequence from the forward primers 
and checking where they appear in the vector sequence used by Imen. 

Let's import the vector sequence that Imen used to design her primers (pUC19):
```{r}
vector_path <- system.file('extdata', 'pUC19_imen.fasta', package = "lambdaPrimeR")
puc19_imen <- read_sequences_noclass(vector_path, input_type = 'vector')
```

We can now locate the vector annealing sequences from each forward primer in the 
pUC19 sequence:

```{r}
insertion_positions <- imen_primers %>%
  mutate(vector_annealing_seq = case_when(
    orientation == 'forward' ~ toupper(vector_annealing_seq),
    orientation == 'reverse' ~ toupper(reverse_complement(vector_annealing_seq))
  )) %>%
  group_by(target_name, orientation) %>%
  do(seq_match = as.tibble(str_locate(puc19_imen$seq, toupper(.$vector_annealing_seq)))) %>%
  unnest()
```

```{r}
insertion_positions
```

There are some interesting results. As we can see on the table above, the coordinates
of the reverse primers vector annealing region matches in the pUC19 sequence are not right
after the matches for the forward primers. That means that Imen designed these 
primers to swap a chunk of the pUC19 sequence between 395-453 bp for the target
sequence.

We can use this coordinates to extract the sequence around the insertion sites 
for each target gene:

```{r}
imen_primers <- left_join(imen_primers, insertion_positions)
imen_primers <- imen_primers %>%
  group_by(target_name, orientation) %>%
  mutate(vector_frag_seq = substr(
    puc19_imen$seq, 
    start-nchar(vector_annealing_seq), 
    end+nchar(vector_annealing_seq)
  ))
```

```{r}
tofile <- imen_primers %>%
  select(target_name, orientation, seq, vector_annealing_seq, target_annealing_seq)
write_csv(tofile, "~/lambdaPrimeR/inst/extdata/imen_primers_toeval.csv")
```

## 05/06/18

### Locating target annealing region on target sequences of `imen_primers`

In order to have a complete `Primer` object after loading primer sequences from 
a .csv file, we need to get the start and end coordinates of the target
annealing regions of each primer:

```{r}
target_anneal_coord <- imen_primers %>%
  select(target_name, target_seq, orientation, target_annealing_seq) %>%
  mutate(target_annealing_seq = case_when(
    orientation == 'forward' ~ toupper(target_annealing_seq),
    orientation == 'reverse' ~ toupper(reverse_complement(target_annealing_seq))
  )) %>%
  group_by(target_name, orientation) %>%
  do(seq_match = as.tibble(str_locate(.$target_seq, toupper(.$target_annealing_seq)))) %>%
  unnest() %>%
  rename(
    target_start = start, 
    target_end = end
  )
```

Adding coordinates to `imen_primers`:

```{r}
imen_primers <- left_join(imen_primers, target_anneal_coord)
```

## 06/01/18

### Redesigning Imen's primers

```{r}
insertion_positions %>%
  group_by(target_name) %>%
  mutate(deletion_length = start[orientation == 'reverse'] - end[orientation == 'forward']-1)
```

```{r}
imen_target_input <- system.file('extdata', 'imen_primer_targets.csv', package = "lambdaPrimeR")
imen_vector_input <- system.file('extdata', 'pUC19_imen.fasta', package = "lambdaPrimeR")

input_pairs <- pimers_table %>%
  select(target_name, vector_name) %>%
  rename(
    target = target_name, 
    vector = vector_name
  )

imen_designs <- read_inputs(imen_target_input, 
                            imen_vector_input, 
                            target_vector_pairs = input_pairs)
```

```{r}
imen_designs <- lapply(imen_designs, function(x)create_primers(x, position = 377, deletion_length = 57))
scores <- lapply(imen_designs, function(x) evaluate_primers(x))
scores <- bind_rows(scores, .id = 'run_id')
```

```{r}
lambdprimer_scores <- scores %>%
  select(-id, -run_id) %>%
  mutate(origin = 'lpr')

imen_scores <- primer_scores_imen %>%
  select(-id) %>%
  mutate(origin = 'imen')

score_comparison <- bind_rows(lambdprimer_scores, imen_scores) %>%
  group_by(primer) %>%
  do(
    ttest = t.test(.$z[.$origin == 'imen'], .$z[.$origin == 'lpr'])
  ) 

score_avg <- bind_rows(lambdprimer_scores, imen_scores) %>%
  group_by(primer, origin) %>%
  summarise(z_sd = sd(z), z = mean(z)) 
```



